Results (Barcelona)

### 2022-01-17 docs/06_results-bcn.Rmd
Change fig size"

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, fig.width=5}

@@

post_cors_participant <- corr_data %>% 
	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
	mutate(
		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
	) %>% 
	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
	geom_tile(na.rm = TRUE) +
	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
	labs(
		x = "Term 1", 
		y = "Term 2", 
		fill = "Posterior\ncorrelation",
		title = "By participant"
	) +
	scale_fill_gradient2(
		low = "#04bf78", mid = "white", high = "#FFC20A", 
		na.value = "white", limits = c(-0.4, 0.4)
	) +
	scale_x_discrete() +
	coord_equal() +
	theme(
		panel.grid = element_blank(),
		legend.position = c(1, 1),
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 6, angle = 90, hjust = 0, vjust = 1),
		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
	)

@@

(post_cors_participant | post_cors_item) &
	plot_layout(guides = "collect") &
	theme(
		panel.grid = element_blank(),
		legend.position = "top",
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1),
		axis.text.y = element_text(size = 7, vjust = 0, hjust = 0)
	)

@@

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4,fig.height=5}

@@

post_cors_participant <- corr_data %>% 
	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
	mutate(
		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
	) %>% 
	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
	geom_tile(na.rm = TRUE) +
	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
	labs(
		x = "Term 1", 
		y = "Term 2", 
		fill = "Posterior\ncorrelation",
		title = "By participant"
	) +
	scale_fill_gradient2(
		low = "#04bf78", mid = "white", high = "#FFC20A", 
		na.value = "white", limits = c(-0.4, 0.4)
	) +
	scale_x_discrete() +
	coord_equal() +
	theme(
		panel.grid = element_blank(),
		legend.position = c(1, 1),
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 6, angle = 90, hjust = 0, vjust = 1),
		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
	)

@@

(post_cors_participant | post_cors_item) &
	plot_layout(guides = "collect") &
	theme(
		panel.grid = element_blank(),
		legend.position = "top",
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1),
		axis.text.y = element_text(size = 7, vjust = 0, hjust = 0)
	)

>>>>

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.height=4}

@@

post_cors_participant <- corr_data %>% 
	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
	mutate(
		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
	) %>% 
	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
	geom_tile(na.rm = TRUE) +
	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
	labs(
		x = "Term 1", 
		y = "Term 2", 
		fill = "Posterior\ncorrelation",
		title = "By participant"
	) +
	scale_fill_gradient2(
		low = "#04bf78", mid = "white", high = "#FFC20A", 
		na.value = "white", limits = c(-0.4, 0.4)
	) +
	scale_x_discrete() +
	coord_equal() +
	theme(
		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
	)

@@

(post_cors_participant | post_cors_item) &
	plot_layout(guides = "collect") &
	theme(
		panel.grid = element_blank(),
		legend.position = "top",
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
	)

@@

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8,fig.height=4}

@@

post_cors_participant <- corr_data %>% 
	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
	mutate(
		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
	) %>% 
	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
	geom_tile(na.rm = TRUE) +
	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
	labs(
		x = "Term 1", 
		y = "Term 2", 
		fill = "Posterior\ncorrelation",
		title = "By participant"
	) +
	scale_fill_gradient2(
		low = "#04bf78", mid = "white", high = "#FFC20A", 
		na.value = "white", limits = c(-0.4, 0.4)
	) +
	scale_x_discrete() +
	coord_equal()  +
	theme(
		axis.text.y = element_text(size = 7)
	)

@@

(post_cors_participant | post_cors_item) &
	plot_layout(guides = "collect") &
	theme(
		panel.grid = element_blank(),
		legend.position = "top",
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)

	)
